Building socket-aware BPF programs

### 2018-10-27 paper/paper.tex
paper: Cite flags extensibility LWN article

New kernel APIs that have any scope for extension should contain a flags
argument. For the socket lookup helpers, a few ideas had been considered as
potential future alternatives to the existing behaviour. The lookup functions
follow the standard socket lookup paths in Linux which have predetermined
methods for selecting a socket when the application uses \verb+SO_REUSEPORT+.
Some subsequent discussion on the mailinglist proposed allowing BPF program
writers to influence the socket selection mechanism~\cite{netdev-sk-select}.

>>>>

New kernel APIs that have any scope for extension should contain a flags
argument~\cite{syscall-flags}. For the socket lookup helpers, a few ideas had
been considered as a potential future alternatives to the existing behaviour.
The lookup functions follow the standard socket lookup paths in Linux which
have predetermined methods for selecting a socket when the application uses
\verb+SO_REUSEPORT+. Some subsequent discussion on the mailinglist proposed
allowing BPF program writers to influence the socket selection
mechanism~\cite{netdev-sk-select}.
